### 2024-05-16 thesis/chapters/03-design.tex
Submit

Fault group separability into clusters is qualitatively analyzed by projecting normalized complete feature sets onto the plain utilizing two principal components. The transformed TD and FD sets are in Figure~\ref{fig:design:pca-complete-sets} with original labels and after low severities are assigned the normal class. The decision boundaries that color the feature space around the data points are determined in 0.02 $times$0.02 square areas by k-NN with five neighbours. We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.

>>>>

Fault group separability into clusters is qualitatively analyzed by projecting normalized complete feature sets onto the plain utilizing two principal components. The transformed TD and FD sets are in Figure~\ref{fig:design:pca-complete-sets} with original labels and after low severities are assigned the normal class. The decision boundaries that color the feature space around the data points are determined in 0.02$\times$0.02 square areas by k-NN with five neighbours. We observe the inability to separate faults by linear boundaries in given feature spaces and the noncompactness of clusters.
